Concurrent Programming in Harmony

### 2021-08-03 book/paper.tex
Latest

>>>>

\begin{figure}
\begin{code}
\harmonysource{bosco2}
\end{code}
\caption{\harmonylink{code/bosco2.hny} Reducing the state space.}
\label{fig:bosco2}
\end{figure}

While one can run this code within little time for $\mathtt{F} = 1$, for
$\mathtt{F} = 2$ the state space to explore is already quite large.
One way to reduce the state space to explore is the following realization:
each processor only considers messages for the round that it is in.
If a message is for an old round, the processor will ignore it;
if a message is for a future round, the processor will buffer it.
So one can simplify the model and have each processor wait
for \emph{all} \texttt{N} messages in a round
instead of $\mathtt{N} - \mathtt{F}$.
It would still have to choose to consider just $\mathtt{N} - \mathtt{F}$
out of those \texttt{N} messages, but executions in which some processors
are left behind in all rounds are no longer considered.
It still includes executions where some subset of $\mathtt{N} - \mathtt{F}$
processors only choose each other messages and essentially ignore the
messages of the remaining \texttt{F} processors, so the resulting model
is just as good.

\autoref{fig:bosco2} shows the code for this model.  Running this with
$\mathtt{F} = 2$ does not take very long and this approach is a good
blueprint for testing other round-based protocols (of which there are
many).
